Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-07 docs/evol.tex
more on the conclusions

We explored the relation between defects with the size of a project version,
measured by the size of its {\sc jar} file by carrying out correlation tests
between the size and the defect counts for each project and its
version. The results, all statistically significant ($p \ll
0.05$) can be seen in Table~\ref{tbl:jarsizecorr}. The {\it Security
  High} category stands out by having a remarkably lower effect than
the other categories, even {\it Security Low} that nearly tops the
list. In essense, a severe bug is introduced only when code that deals with
untrusted input is introduced in a application.

@@

In this work we analyzed a large software repository to examine the behavior
of security bugs. Specifically, we analyzed more than 260GB of interdependent
projcet versions to see how security bugs evolve over time, their
persistence, and their relation with other bug categories and the size in
terms of bytecode.

Our work could (?) aid bug-prediction models in the same way as~\cite{BN11}.

>>>>

We explored the relation between defects with the size of a project version,
measured by the size of its {\sc jar} file by carrying out correlation tests
between the size and the defect counts for each project and its
version. The results, all statistically significant ($p \ll
0.05$) can be seen in Table~\ref{tbl:jarsizecorr}. The {\it Security
  High} category stands out by having a remarkably lower effect than
the other categories, even {\it Security Low} that nearly tops the
list.

@@

In this work we analyzed a large software repository to examine the behavior
of security bugs. Specifically, we analyzed more than 260GB of interdependent
projcet versions to see how security bugs evolve over time, their
persistence, and their relation with other bug categories and the size in
terms of bytecode. We have to mentioned that the versions examined were
actually releases of these projets. In essence, these {\sc jar}s were the ones
that were or still are out there in the wild, being used either as
applications, or dependencies of others.

Our primary expectation was that security bugs and especially severe
ones, should be corrected as projects evolve. But our findigs indicate that this is
not true. Concerning bug persistence, we saw that the behaviour of security
bugs is similar to the other categories. We have to point out the fact that
having an average of two to three versions persistence in a sample where 60\%
of the projects have three versions, is not a positive result especially in the
case of the {\it Security High} bugs. An interesting observation was that
the relation between severe security bugs and a project's size the is different
than the other categories. In essense, a severe bug is introduced only when code
that deals with untrusted input is added in a application. Furthermore, the
pairwise correlations between all categories indicated that severe bugs are
coming from a special kind of carelessness. Finally, it is interesting to see
that security bugs were one of the top two bug categories existing in such a
large ecosystem.
